Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory

### 2017-07-25 writing/paper-Tian-gr-wetting.tex
Minor change

% Created 2017-07-22 Sat 15:09
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
\date{}
\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
\begin{document}

@@

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
  potential of 2D materials represents the crucial first step for understanding their wettability.
  Here we develop the first theoretical framework to model the wettability of the doped 2D 
  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
  including: (i) the change of 2D materials surface energy (atomistic scale), 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
  as well as the molecular packing behavior on a 2D material-coated surface, 
  essentially facilitating the interfacial engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Introduction}
\label{sec:org828e535}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties
\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress
in the scalable production of large-area 2D materials
\cite{Boott_2015,Li_2016} has paved the way for the applications of
functional surfaces and ultrathin membranes
\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
The concept of van der Waals (vdW) epitaxy has been further extended
to grow molecular heterostructures on 2D material-coated surfaces for
a variety of applications
\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
realization of these technologies essentially requires precise control
over the molecular interactions at 2D material interfaces, which
motivates fundamental research of their interfacial properties, in
particular the wettability.  An accurate determination of the
interfacial tension, nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) radius is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOS) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
in the \textit{ab initio} calculations and scanning tunneling
microscopy (STM) studies on the adsorbed molecules on graphene
\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
doping-dependent vdW interactions. Subsequently, the doping-induced
change in the wettability of graphene has been observed in the
contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
this respect, however, most reports described the doping-dependent
wettability with the basic Young-Lippmann equation (YLE)
\cite{Lippmann_1875}, whereas the interplay between the orientation of
liquid molecules at the interface \cite{Shen_2006} and the electronic
structure of the 2D materials is often ignored. In order to address
the discrepancies among the literature, a general and complete
theoretical picture that bridges the gap between different length
scales, is clearly required.

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are considered,
as shown in Figure \ref{fig:scheme-method}. At the atomistic scale, we
formulate the dependence of surface energy of a 2D material on the
doping density using the quantum capacitance (QC) calculated by the
density functional theory (DFT). Next, the surface-charge-induced
reorientation of liquid molecules adjacent to the interface is
associated with an N-body system, which is resolved by molecular
dynamics (MD) simulations, allowing quantification of the interfacial
tension in the absence of electrolytes in liquid. The effect of the
electrical double layer (EDL) induced by the electrostatic
interactions between the 2D material surface charges and the ionic
species in liquid, is then addressed at the continuum level. Practical
considerations, such as the defect density and the surface
contamination are also taken into account to provide a comprehensive
understanding of the phenomena. Finally, we examine and validate our
theory by comparing with the contact angle changes reported in the
electrowetting and the substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:orgc095477}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:org28f87f6}

Consider a liquid (\emph{L}) droplet sitting on a flat, monolayer 2D
material (\emph{2D}) supported by a solid substrate, following the Young’s
equation, the change of the equilibrium contact angle \(\theta\) upon
doping, is given by
\begin{equation}
\label{eqn-def-Young-Delta-theta}
\gamma_{\mathrm{L}} \Delta \cos\theta = \Delta \gamma_{\mathrm{2D}}
                                 - \Delta \gamma_{\mathrm{2D-L}}
\end{equation}
where \(\gamma_{\mathrm{L}}\) and \(\gamma_{\mathrm{2D}}\) are the surface
tensions of liquid and the 2D material considered,
respectively, \(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the
liquid and the contacting 2D material. We define \(\Delta \gamma =
\gamma - \gamma_{0}\) for all the surface (interfacial) tensions considered and
\(\Delta \cos \theta = \cos \theta - \cos \theta_{0}\), where the
subscript 0 corresponds to that in the case of intrinsic 2D material,
with the doping density per unit area, \(\sigma_{\mathrm{2D}} = 0\). In
the theoretical analysis presented here, we aim to model \(\Delta \cos
\theta\) as a function of \(\sigma_{\mathrm{2D}}\). Note that under the
assumptions that (i) the change of \(E_{\mathrm{F}}\) in the doped 2D
materials does not result in the interfacial electron transfer,
namely, the electrochemical reactions, (ii) the doping effect does not
change the surface energy of the underlying substrate, and (iii) the
vdW and electrostatic interactions are perfectly additive and
pairwise, one can decouple the effect of the underlying
substrate. Therefore the debate of the “wetting transparency”
\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our analysis.

@@

Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
2D materials considered here. Clearly, the doping of 2D materials
reduces their surface energy, or based on the classical definition,
the work required to separate two stacked monolayers is lowered. Among
the 2D materials, we find that graphene shows the highest degree of
surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
\textasciitilde{}20\% reduction of its intrinsic surface tension
\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) = \(\pm
4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\). However, as will be
discussed later, it does not imply a reduced wettability because the
quantum capacitance effect also reduces the interfacial tension,
\(\gamma_{\mathrm{2D-L}}\). A clear trend is that the surface energy
decrease is more significant in the 2D semimetals (e.g. graphene,
silicene, and germanene) than that in the 2D semiconductors
(e.g. TMDCs). This reflects the fact that the effective mass of
carriers in the 2D semiconductors is much higher than that in the 2D
semimetals \cite{davies_two-dimensional_1997}, thereby resulting in
high DOS, as well as a high \(C_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains why the
surface energy decrease for silicene and germanene are lower than
that for graphene \cite{Yan_2013}.  To our knowledge, the doping-induced
surface energy change in 2D materials has never been investigated
experimentally, which may be of interest for future study.

\subsection{Reorientation of Liquid Molecules}
\label{sec:org8d3c56f}

@@

Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and
its contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\))
and Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as
functions of \(\sigma_{\mathrm{2D}}\). We note that the change of
adhesion energy in the doped graphene system is dominated by the
Coulombic interaction. When the doping level of graphene is \(\pm 4
\times 10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction
causes a decrease in the adhesion energy of \textasciitilde{} -15 mJ\(\cdot
\mathrm{m}^{-2}\), while the vdW interaction, on the other hand, causes
a slight increase in the adhesion energy by less than 5 mJ\(\cdot
\mathrm{m}^{-2}\). In other words, concerning the reorientation of
water molecules at large doping levels, the Coulombic interaction
favors the decrease of \(\gamma_{\mathrm{2D-L}}\), and thus the contact
angle \(\theta\), while the vdW interaction slightly increases
\(\gamma_{\mathrm{2D-L}}\) and \(\theta\). We shall note that due to the
highly polar nature of water molecules, the average inter-molecular
equilibrium distance in the absence of external electric field
(\(r_{\mathrm{O-O}}=2.75\ \mathrm{\AA}\)) is shorter than the
Lennard-Jones equilibrium distance (\(r_{\mathrm{O-O}}=3.16\
\mathrm{\AA}\)) \cite{Mark_2001}. Increasing the doping density of the
graphene sheet essentially enhances the Coulombic attractions between
graphene and water molecules, further reducing the inter-molecular
equilibrium distance, as seen in Figure S2(a), the distance between
the first water layer and graphene (calculated from maximal
\(\rho_{\mathrm{L}}\) from Figure \ref{fig:MD-res}(d)) slightly decreases
in doped graphene systems, compared with the charge-neutral system,
which eventually leads to a slight increase in \(\Delta
\Phi_{\mathrm{LJ}}\).  The plot of \(\Delta \Phi\) as a function of
\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(c) shows an apparent
asymmetric behavior. This can be further revealed from the
\emph{z}-dependent local molecular density \(\rho_{\mathrm{L}}\) and charge
density \(\delta_{\mathrm{L}}\) profiles of the water molecules, as
shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(e),
respectively. The molecular density of the first water layer adjacent
to graphene increases when graphene is p-doped
(\(\sigma_{\mathrm{2D}}=0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently 4.56 \textit{e}/atom) and decreases when graphene is
n-doped (\(\sigma_{\mathrm{2D}}=-0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently -4.56 \textit{e}/atom) compared with the case of
charge-neutral graphene, indicating the polarity-dependent adsorption
of water molecules on graphene: lighter H atoms prefer to adsorb onto
n-doped graphene electrostatically. Similar trend can also be observed
in the \(\delta_{\mathrm{L}}\) (Figure \ref{fig:MD-res}(e))and water
dipole orientation \(\cos \mu\) (Figure S1) profiles, both
suggesting that water orientation depends strongly on
\(\sigma_{\mathrm{2D}}\): more negative \(\sigma_{\mathrm{2D}}\) tends
to orient the water dipoles more towards the 2D interface, reflected
by the more positive charge densities due to first-layer H atoms, and
the more negative \(\cos \mu\) values. Interestingly, the \(\Delta
\Phi_{\mathrm{Coul}}\) exhibits small positive contribution for slightly
n-doped graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\
e\cdot \mathrm{cm}^{-2}\) or equivalently -0.76 \textit{e}/atom,
indicating that the reorientation of interfacial water molecules by
small negative charges on graphene helps minimizing the Coulombic
interactions. The trend observed in hydrogen-bond densities (see
Figure S3) also matches those observed in \(\rho_{\mathrm{L}}\),
\(\delta_{\mathrm{L}}\) and \(\cos \mu\) profiles.

@@

\subsection{Electrical Double Layer Effect}
\label{sec:orgc5ae7c8}

@@

The above analysis leads to two important observations: (i) If a thin
contamination layer (usually composed of charge-neutral hydrocarbon
species \cite{li_effect_2013}) exists between the Helmholtz layer and
the 2D material surface, the electroneutrality at the interface (eq
\ref{eqn-neutrality}) still holds, such that \((\Delta \cos
\theta)^{\mathrm{EDL}}\) remains the same (see eq
\ref{eqn-Delta-cos-EDL-final}). In other words, despite the recent
debate about the role of the airborne adsorbates in the contact angle
measurement on 2D materials
\cite{li_effect_2013,Kozbial_2015,Xu_2013_withwhat,Chow_2015}, we expect
that the experimental characterization of the doping-induced contact
angle change is more robust and reproducible. (ii) As shown in eqs
\ref{eqn-GCS-capacitance-series} and \ref{eqn-Delta-gamma-2DL-EDL-full},
the equivalent capacitance in the YLE, \(C_{\mathrm{YL}}\), is not
identical to the total capacitance in the EDL, \(C_{\mathrm{EDL}}\). We
notice that the literature in this field (e.g. Refs.
\citenum{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016})
often simply assumed that \(C_{\mathrm{YL}}=C_{\mathrm{DH}}\) in the
YLE, which significantly overestimates \((\Delta cos
\theta)^{\mathrm{EDL}}\), when \(\psi_{\mathrm{2D}} \gg
k_{\mathrm{B}}T/e\) \cite{israelachvili03_inter}, as can be found in heavily-doped 2D materials.

@@

\subsection{Practical Considerations}
\label{sec:orgeba1656}

@@

An interesting implication is that, together with the recent
development in engineering 2D materials’ wetting translucency
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
in principle, upon doping, a 2D material becomes less “transparent” (or more screening)
to both van der Waals and Coulombic interactions exerted from the underlying
substrate, due to enhanced liquid-2D material interactions. That is to say, the doping level can be
another control variable to modulate the molecular packing and
epitaxial behavior on a 2D material-coated surface, which may bring
new technology opportunity for a variety of applications.

\section{Conclusion}
\label{sec:org258c77f}

@@

\newpage{}
\section{Figures}
\label{sec:orgb7fbb04}

>>>>

% Created 2017-07-24 Mon 23:13
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

@@

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials
  interfaces enables new technological opportunities in functional
  surfaces and molecular epitaxy.  Understanding the wettability of 2D
  materials represents the crucial first step towards quantifying the
  interplay between the interfacial forces and electric potential of
  2D materials interfaces.  Here we develop the first theoretical
  framework to model the wettability of the doped 2D materials by
  properly bridging the multiscale physical phenomena at the 2D
  interfaces, including: (i) the change of 2D materials surface energy
  (atomistic scale, several \AA), (ii) the molecular reorientation of
  liquid molecules adjacent to the interface (molecular scale,
  \(10^{0}\) \sim \(10^{1}\) nm), and (iii) the electrical double layer
  (EDL) formed in the liquid phase (mesoscopic scale,
  \(10^{0}\) \sim \(10^{4}\) nm).  The latter two effects are found to
  be the major mechanisms responsible for the contact angle change
  upon doping.  When the doping level is electrostatically tuned, we
  demonstrate that 2D materials with high quantum capacitances (e.g.,
  transition metal dichalcogenides, TMDCs) possess a wider range of
  tunability in the interfacial tension.  Furthermore, practical
  considerations such as defects and airborne contamination are also
  quantitatively discussed.  Our analysis implies that the doping
  level can be another variable to modulate the wettability at 2D
  materials interfaces, as well as the molecular packing behavior on a
  2D material-coated surface, essentially facilitating the interfacial
  engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Introduction}
\label{sec:org5097ce2}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties
\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress
in the scalable production of large-area 2D materials
\cite{Boott_2015,Li_2016} has paved the way for the applications of
functional surfaces and ultrathin membranes
\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
The concept of van der Waals (vdW) epitaxy has been further extended
to grow molecular heterostructures on 2D material-coated surfaces for
a variety of applications
\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
realization of these technologies essentially requires precise control
over the molecular interactions at 2D material interfaces, which
motivates fundamental research of their interfacial properties, in
particular the wettability.  An accurate determination of the
interfacial tension, nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) radius is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOS) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
in the \textit{ab initio} calculations and scanning tunneling
microscopy (STM) studies on the adsorbed molecules on graphene
\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
doping-dependent vdW interactions. Subsequently, the doping-induced
change in the wettability of graphene has been observed in the
contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
this respect, however, most reports described the doping-dependent
wettability with the basic Young-Lippmann equation (YLE)
\cite{Lippmann_1875}. The interplay between the orientation of
liquid molecules at the interface \cite{Shen_2006} and the electronic
structure of the 2D materials is often ignored. In order to address
the discrepancies among the literature, a general and complete
theoretical picture that bridges the gap between different length
scales, is clearly required.

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are considered,
as shown in Figure \ref{fig:scheme-method}. At the atomistic scale
(several \AA{}), we formulate the dependence of surface energy of a 2D
material on the doping density using the quantum capacitance (QC)
calculated by the hybrid density functional theory (DFT) at the level
of Heyd-Scuseria-Ernzerhof functionals (HSE06). Next, the
surface-charge-induced reorientation of liquid molecules adjacent to
the interface is associated with an N-body system, which is resolved
by molecular dynamics (MD) simulations, allowing quantification of the
interfacial tension in the absence of electrolytes in liquid at the
molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm). The effect of the electrical
double layer (EDL) induced by the electrostatic interactions between
the 2D material surface charges and the ionic species in liquid, is
then addressed at the continuum level (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm). Practical
considerations, such as the defect density and the surface
contamination are also taken into account to provide a comprehensive
understanding of the phenomena. Finally, we examine and validate our
theory by comparing with the contact angle changes reported in the
electrowetting and the substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:org177ad24}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:orge414c66}

Consider a liquid (\emph{L}) droplet sitting on a flat, monolayer 2D
material (\emph{2D}) supported by a solid substrate, following the Young’s
equation, the change of the equilibrium contact angle \(\theta\) upon
doping, is given by
\begin{equation}
\label{eqn-def-Young-Delta-theta}
\gamma_{\mathrm{L}} \Delta \cos\theta = \Delta \gamma_{\mathrm{2D}}
                                 - \Delta \gamma_{\mathrm{2D-L}}
\end{equation}
where \(\gamma_{\mathrm{L}}\) and \(\gamma_{\mathrm{2D}}\) are the surface
tensions of liquid and the 2D material considered, respectively,
\(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the liquid
and the contacting 2D material. We define \(\Delta \gamma = \gamma -
\gamma_{0}\) for all the surface (interfacial) tensions considered and
\(\Delta \cos \theta = \cos \theta - \cos \theta_{0}\), where the
subscript 0 corresponds to that in the case of intrinsic 2D material,
with the doping density per unit area, \(\sigma_{\mathrm{2D}} = 0\). In
the theoretical analysis presented here, we aim to model \(\Delta \cos
\theta\) as a function of \(\sigma_{\mathrm{2D}}\). Note that under the
assumptions that (i) the change of \(E_{\mathrm{F}}\) in the doped 2D
materials does not result in the interfacial electron transfer,
namely, the electrochemical reactions, (ii) the doping effect does not
change the surface energy of the underlying substrate, and (iii) the
vdW and electrostatic interactions are perfectly additive and
pairwise, one can decouple the effect of the underlying
substrate. Therefore the debate of the “wetting transparency”
\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our
analysis of \(\Delta \cos \theta\), which is independent of \(\gamma_{0}\)
or \(\theta_{0}\).

@@

Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
2D materials considered here. Clearly, the doping of 2D materials
reduces their surface energy, or based on the classical definition,
the work required to separate two stacked monolayers is lowered. Among
the 2D materials, we find that graphene shows the highest degree of
surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or \textasciitilde{}20\%
reduction of its intrinsic surface tension \cite{shih_wetting_2013}, at
\(\sigma_{\mathrm{2D}}\) = \(\pm 4\times10^{13}\ e\cdot
\mathrm{cm}^{-2}\). However, as will be discussed later, it does not
imply a reduced wettability because the quantum capacitance effect
also reduces the interfacial tension, \(\gamma_{\mathrm{2D-L}}\). A
clear trend is that the surface energy decrease is more significant in
the 2D semimetals (e.g. graphene, silicene, and germanene) than that
in the 2D semiconductors (e.g. TMDCs). This reflects the fact that the
effective mass of carriers in the 2D semiconductors is much higher
than that in the 2D semimetals \cite{davies_two-dimensional_1997},
thereby resulting in high DOS, as well as a high \(C_{\mathrm{2D}}\)
(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains
why the surface energy decrease for silicene and germanene are lower
than that for graphene \cite{Yan_2013}.  To our knowledge, the
doping-induced surface energy change in 2D materials has never been
investigated experimentally, which may be of interest for future
study, inspired by the recent advances in direct measurement of 2D
material surface energy \cite{van_Engers_2017_direct_surf_gr}.

\subsection{Reorientation of Liquid Molecules}
\label{sec:org8e3e719}

@@

Figure \ref{fig:MD-res}(c) shows the calculated \(\Delta \Phi\), and
its contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\))
and Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as
functions of \(\sigma_{\mathrm{2D}}\). We note that the change of
adhesion energy in the doped graphene system is dominated by the
Coulombic interaction. When the doping level of graphene is \(\pm 4
\times 10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction
causes a decrease in the adhesion energy of \textasciitilde{} -15 mJ\(\cdot
\mathrm{m}^{-2}\), while the vdW interaction, on the other hand, causes
a slight increase in the adhesion energy by less than 5 mJ\(\cdot
\mathrm{m}^{-2}\). In other words, concerning the reorientation of
water molecules at large doping levels, the Coulombic interaction
favors the decrease of \(\gamma_{\mathrm{2D-L}}\), and thus the contact
angle \(\theta\), while the vdW interaction slightly increases
\(\gamma_{\mathrm{2D-L}}\) and \(\theta\). We shall note that due to the
highly polar nature of water molecules, the average inter-molecular
equilibrium distance in the absence of external electric field
(\(r_{\mathrm{O-O}}=2.75\ \mathrm{\AA}\)) is shorter than the
Lennard-Jones equilibrium distance (\(r_{\mathrm{O-O}}=3.16\
\mathrm{\AA}\)) \cite{Mark_2001}. Increasing the doping density of the
graphene sheet essentially enhances the Coulombic attractions between
graphene and water molecules, further reducing the inter-molecular
equilibrium distance, as seen in Figure S2(a), the distance between
the first water layer and graphene (calculated from maximal
\(\rho_{\mathrm{L}}\) from Figure \ref{fig:MD-res}(d)) slightly decreases
in doped graphene systems, compared with the charge-neutral system,
which eventually leads to a slight increase in \(\Delta
\Phi_{\mathrm{LJ}}\).  The plot of \(\Delta \Phi\) as a function of
\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(c) shows an apparent
asymmetric behavior. This can be further revealed from the
\emph{z}-dependent local molecular density \(\rho_{\mathrm{L}}\) and charge
density \(\delta_{\mathrm{L}}\) profiles of the water molecules, as
shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(e),
respectively. The molecular density of the first water layer adjacent
to graphene increases when graphene is p-doped
(\(\sigma_{\mathrm{2D}}=0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently 4.56 \textit{e}/atom) and decreases when graphene is
n-doped (\(\sigma_{\mathrm{2D}}=-0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently -4.56 \textit{e}/atom) compared with the case of
charge-neutral graphene, indicating the polarity-dependent adsorption
of water molecules on graphene: lighter H atoms prefer to adsorb onto
n-doped graphene electrostatically. Similar trend can also be observed
in the \(\delta_{\mathrm{L}}\) (Figure \ref{fig:MD-res}(e))and water
dipole orientation \(\cos \mu\) (Figure S1) profiles, both
suggesting that water orientation depends strongly on
\(\sigma_{\mathrm{2D}}\): more negative \(\sigma_{\mathrm{2D}}\) tends
to orient the water dipoles more towards the 2D interface, reflected
by the more positive charge densities due to first-layer H atoms, and
the more negative \(\cos \mu\) values. Interestingly, the \(\Delta
\Phi_{\mathrm{Coul}}\) exhibits small positive contribution for slightly
n-doped graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\
e\cdot \mathrm{cm}^{-2}\) or equivalently -0.76 \textit{e}/atom,
indicating that the reorientation of interfacial water molecules by
small negative charges on graphene helps minimizing the Coulombic
interactions. The trend observed in hydrogen-bond densities (see
Figure S3) also matches those observed in \(\rho_{\mathrm{L}}\),
\(\delta_{\mathrm{L}}\) and \(\cos \mu\) profiles.

@@

\subsection{Electrical Double Layer Effect}
\label{sec:org689b84b}

@@

The above analysis leads to two important observations: (i) If a thin
contamination layer (usually composed of charge-neutral hydrocarbon
species \cite{li_effect_2013}) exists between the Helmholtz layer and
the 2D material surface, the electroneutrality at the interface (eq
\ref{eqn-neutrality}) still holds, such that \((\Delta \cos
\theta)^{\mathrm{EDL}}\) remains the same (see eq
\ref{eqn-Delta-cos-EDL-final}). In other words, despite the recent
debate about the role of the airborne adsorbates in the contact angle
measurement on 2D materials
\cite{li_effect_2013,Kozbial_2015,Xu_2013_withwhat,Chow_2015}, we expect
that the experimental characterization of the doping-induced contact
angle change is more robust and reproducible. (ii) As shown in eqs
\ref{eqn-GCS-capacitance-series} and \ref{eqn-Delta-gamma-2DL-EDL-full},
the equivalent capacitance in the YLE, \(C_{\mathrm{YL}}\), is not
identical to the total capacitance in the EDL, \(C_{\mathrm{EDL}}\). We
notice that the literature in this field (e.g. Refs.
\citenum{ostrowski_tunable_2014,daub_electrowetting_2007,goniszewski_correlation_2016,ashraf_doping-induced_2016})
often simply assumed that \(C_{\mathrm{YL}}=C_{\mathrm{DH}}\) in the
YLE, which significantly overestimates \((\Delta \cos
\theta)^{\mathrm{EDL}}\), when \(\psi_{\mathrm{2D}} \gg
k_{\mathrm{B}}T/e\) \cite{israelachvili03_inter}, as can be found in heavily-doped 2D materials.

@@

\subsection{Practical Considerations}
\label{sec:orgf8df8eb}

@@

An interesting implication is that, together with the recent
development in engineering 2D materials’ wetting translucency
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
in principle, upon doping, a 2D material becomes less “transparent” (or more screening)
to both van der Waals and Coulombic interactions exerted from the underlying
substrate, due to enhanced liquid-2D material interactions. That is to say, the doping level can be
another control variable to modulate the molecular packing and
epitaxial behavior on a 2D material-coated surface, which may bring
new technological opportunity for a variety of applications.

\section{Conclusion}
\label{sec:org950fc3c}

@@

\newpage{}
\section{Figures}
\label{sec:org801860f}
